Graph Generators: State of the Art and Open Challenges

### 2019-06-14 generators_general.tex
added strengths and weaknesses for general graph generators

We start by focusing on approaches that have been designed for dealing with the generation of general graph
data that is not aimed at a particular application domain. Currently, there exists a
number of tools which involve a kind of general graph data generator, such as
gtools from projects nauty and Traces~\cite{gtools} or the Stanford
GraphBase~\cite{GraphBase}. We, however, focus on primarily
generating/benchmarking projects targeting the Big Data world.

@@

>>>>

We start by focusing on approaches that have been designed for dealing with the
generation of general graph data that is not aimed at a particular application
domain. In general, such generators focus on reproducing properties observed in
real graphs regardless of their domain such as the degree distribution, the
diameter, the presence of a large connected component, a community structure or
a significantly large clustering coefficient.

%Currently, there exists a number of tools which involve a kind of
%general graph data generator, such as gtools from projects nauty and
%Traces~\cite{gtools} or the Stanford GraphBase~\cite{GraphBase}. We, however,
%focus on primarily generating/benchmarking projects targeting the Big Data
%world.

@@

\paragraph{Strengths and Weaknesses of General Graph Generators}
In general, existing general graph generators produce graphs with the following
properties: skewed degree distribution (e.g. powerlay), small diameter, large
clustering coefficient, a large largest connected component and some degree of
community structure. Degree distribution can be typically configured while other
properties are just a result of the genration process and cannot be controlled
by any means.

This is not the case of BTER and Darwini which besides the degree distribution,
they also allow tunning the clustering coefficient. However, some use cases
demand for more control on the characteristics of the generated graphs.
This is the case, for instance, of benchmarking, where the underlying graph
structure has direct implications to the performance of the graph algorithms
to run. For this reason, the design of graph generators with the capability of fine
tunning the characteristics of the generated graphs still remains as an open
challenge. The question that remains though is what characteristics to tune,
and which are the algorithms whose depends on such characteristics.
